---
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(quantmod)
library(PerformanceAnalytics)
```

#### Index

* Section I of this document will examine current capital market conditions. 
* Section II will examine current macroeconomic conditions. 
* Section III will discuss underlying economic theory to serve as a platform for forward looking discussion about capital markets (allocation, position sizing).
* Section IV will contain forward looking thoughts and technical decomposition. 

#### Section I - Capital Markets

In order to be concise we will examine ETF's of broad asset classes based in the U.S:

* Cash Equivalents ('SHV')
* U.S. Large-Cap Stocks ('SPY')
* U.S. Treasury Bonds ('TLT')
* U.S. Real Estate ('VNQ')
* Diversified Commodities ('DBC')

```{r}
asset_tickers <- c("SHV", "SPY", "TLT", "VNQ", "DBC")
getSymbols(asset_tickers, from = "2009-01-01")
SHV_ret <- monthlyReturn(SHV)
SPY_ret <- monthlyReturn(SPY)
TLT_ret <- monthlyReturn(TLT)
VNQ_ret <- monthlyReturn(VNQ)
DBC_ret <- monthlyReturn(DBC)
assets_ret <- cbind(SHV_ret, SPY_ret, TLT_ret, VNQ_ret, DBC_ret)
assets_ret <- `colnames<-`(assets_ret, c("SHV Returns", "SPY Returns", "TLT Returns", "VNQ Returns", "DBC Returns"))
charts.PerformanceSummary(R = assets_ret, main = "Asset Class Returns", wealth.index = TRUE)
charts.RollingPerformance(assets_ret)
table.AnnualizedReturns(assets_ret)
chart.Drawdown(assets_ret, legend.loc = "bottomleft", main = "Asset Class Drawdowns")
chart.Correlation(assets_ret)
```

We can view Annualized Return vs. Annualized StdDev through time for each instrument, with lines as Sharpe Ratio values of 1,2,3:

```{r}
chart.SnailTrail(SHV_ret, main = "Cash Equivalent")
chart.SnailTrail(SPY_ret, main = "U.S Large-Cap Stocks")
chart.SnailTrail(TLT_ret, main = "U.S. Treasury Bonds")
chart.SnailTrail(VNQ_ret, main = "U.S. Real Estate")
chart.SnailTrail(DBC_ret, main = "Diversified Commodities")
```

---

#### Section II - Macroeconomic Data

We will examine broad macroeconomic data:

* Effective Federal Funds Rate
* Real GDP % Change
* Employment
* Smoothed U.S. Recession Probabilities
    + [https://pages.uoregon.edu/jpiger/research/published-papers/chauvet-and-piger_2008_jour.pdf]
* 

```{r}
macro_symbols <- c("EFFR", "GDPC1", "UNRATE", "RECPROUSM156N")
getSymbols(macro_symbols, src = "FRED", from = "2009-01-01")
plot(EFFR, main = "Effective Federal Funds Rate")
GDPC1 <- GDPC1[249:289,]
plot(ROC(GDPC1), type = "h", main =  "Real GDP %-Change")
UNRATE <- UNRATE[733:855,]
plot(UNRATE)
REC_PROB <- RECPROUSM156N
REC_PROB <- REC_PROB[391:622,]
REC_PROB <- `colnames<-`(REC_PROB, "Recession Probability (%)")
plot(REC_PROB, main = "Smoothed U.S. Recession Probability")
last(REC_PROB)
```

---

#### Section III - Theory



